A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 textos/dsrt/engaoi.tex
eng

A key problem in the peer-to-peer architectures, in what concerns the use of interest management, is that some peers are responsible for part of the simulation and for decide to whom each state update would interest. Assuming that there are only trustable players, the interest management technique may be useful. However, supposing that a player is malicious, he could hack his client software and avoid sending state updates to certain players, who would be prejudiced in the game. Consequently, the distributed server model is considered more suitable to use the interest management technique.

@@

\textbf{Avatar} is the player representation in the virtual environment. Through his avatar, the player interacts with the game world and with the other players. Examples of avatars are the characters in MMORPG games like World of Warcraft.

@@

This work is based on a virtual environment partitioned into regions, each managed by a server. The regions are contiguous, exploring the locality of the players' avatars. Thus, avatars next to each other will probably be located in the same region and, therefore, their clients will tend to be connected to the same server, so that their interaction is faster (Fig. \ref{partitions}). Situations in which players interacting with each other are connected to different servers imply a higher bandwidth usage, as it is required some sort of negotiation between the servers to which the different players are connected, in order to maintain the states of simulation in both servers identical. Also, the hop count of each message between these clients is increased, since there is one more intermediary.

@@

\subsection{Ângulo de visão}
\label{angle}

Outra maneira, um pouco mais refinada, de gerenciar o interesse dos avatares consiste em levar em conta o que o jogador pode visualizar, ou seja, seu ângulo de visão. A área dentro de onde esse jogador perceberá mudanças relevantes pode ser definida como um setor de círculo. É similar à área em formato de círculo definida anteriormente, porém leva em consideração que o jogador só pode visualizar objetos que estão situados à frente de seu avatar.

%pegar isso pra mim!?... CLARO! fui eu que fiz!
Uma questão a ser considerada, no entanto, é que o jogador não irá receber atualizações de estado de entidades imediatamente atrás de seu avatar, podendo compromenter o jogo. Se o avatar girar 180° em torno de seu próprio eixo rapidamente, pode ser que não veja determinada entidade que deveria estar ali, necessitando de certo tempo para receber o estado dela. Isto acontece porque, apesar desta entidade ter estado próximo do avatar, ele não recebeu suas informações ainda pois antes ela estava atrás dele, fora do seu campo de visão. Na figura \ref{fangle} é ilustrado como seria uma área de interesse que levaria em consideração o campo de visão do jogador.

>>>>

A key problem in the peer-to-peer architectures, in what concerns the use of interest management, is that some peers are responsible for part of the simulation and for decide to whom each state update would interest. Assuming that there are only trustable players, the interest management technique may be useful. However, supposing that a player is malicious, he could hack his client software and avoid sending state updates to certain players, who would be in disadvantage. Consequently, the distributed server model is considered more suitable to use the interest management technique.

@@

\textbf{Avatar} is the player representation in the virtual environment. Through his avatar, the player interacts with the game world and with the other players. Examples of avatars are the characters in MMORPG (massively multiplayer online role-playing games) games like World of Warcraft.

@@

This work is based on a virtual environment partitioned into regions, each managed by a server. The regions are contiguous, exploring the locality of the players' avatars. Thus, avatars next to each other will probably be located in the same region and, therefore, their clients will tend to be connected to the same server, so that their interaction is faster (Fig. \ref{partitions}). Situations in which two players interacting with each other are connected to different servers imply a higher bandwidth usage, as it is required some sort of negotiation between the servers to which the different players are connected, in order to maintain the states of simulation in both servers identical. Also, the hop count of each message between the clients of these players is increased, since there is one more intermediary.

@@

\subsection{Field of view}
\label{angle}

A more refined method to manage the interests of the avatars is to take into account what each player can see. The area within which the player perceives state changes can be defined as a circular sector. This is similar to the circular area of interest described in the previous section, but takes into account that the player can only see objects that are located in front of his avatar.

%pegar isso pra mim!?... CLARO! fui eu que fiz!

One issue to be considered, however, is that the player will not receive state updates from entities entities which are close to his avatar, but behind it. This could cause some problems. For example, if the avatar turns 180 degrees, the player might not see a particular entity that should be there, needing some time to receive its state information. This happens because, despite this entity have been near the avatar, he did not receive its information yet because it was behind him, outside his field of view. In figure \ref{fangle} it is illustrated an area of interest that takes into account the player's view angle.

Uma questão a ser considerada, no entanto, é que o jogador não irá receber atualizações de estado de entidades imediatamente atrás de seu avatar, podendo compromenter o jogo. Se o avatar girar 180° em torno de seu próprio eixo rapidamente, pode ser que não veja determinada entidade que deveria estar ali, necessitando de certo tempo para receber o estado dela. Isto acontece porque, apesar desta entidade ter estado próximo do avatar, ele não recebeu suas informações ainda pois antes ela estava atrás dele, fora do seu campo de visão. Na figura \ref{fangle} é ilustrado como seria uma área de interesse que levaria em consideração o campo de visão do jogador.
